Seismic Time Series Analysis\\Statistics for Spatio-Temporal Data\\\textit{-- project draft --}

### 2020-06-06 draft.tex
fix plot numbers

\begin{figure}[h]
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=\linewidth]{project.uccs_files/figure-latex/arima-26} %30
		\caption{ACF and PACF plots}
		\label{fig:arima-26}
	\end{subfigure}
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=\linewidth]{project.uccs_files/figure-latex/arima-24} %28
		\caption{Q-Q plot}
		\label{fig:arima-24}
	\end{subfigure}
	\begin{center}
		\caption{Plots for $\mathrm{ARIMA}(2,0,0)(0,1,1)_{168}$}
		\label{fig:arima}
	\end{center}
\end{figure}

@@

\begin{figure}[h]
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=1\linewidth]{project.uccs_files/figure-latex/arima-27} %32
		\caption{$\mathrm{ARIMA}(2,0,0)(0,1,1)_{168}$}
		\label{fig:arima-forecast:200011}
	\end{subfigure}
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=1\linewidth]{project.uccs_files/figure-latex/arima-51} %60
		\caption{$\mathrm{ARIMA}(3,1,1)(0,1,1)_{168}$}
		\label{fig:arima-forecast:412011}
	\end{subfigure}
	\begin{center}
		\caption{ARIMA forecasts}{\footnotesize$\mathrm{ARIMA}(4,1,2)(0,1,1)_{168}$ behaves like $\mathrm{ARIMA}(3,1,1)(0,1,1)_{168}$ with faster increasing variablity}
		\label{fig:arima-forecast}
	\end{center}
\end{figure}

@@

\begin{figure}[h]
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=1\linewidth]{"project.mems_files/figure-latex/arima-18"} %15
		\caption{$\mathrm{ARIMA}(0,1,1)(0,1,1)_{168}$}
		\label{fig:mems:arima:011011}
	\end{subfigure}
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=1\linewidth]{"project.mems_files/figure-latex/arima-11"} %9
		\caption{$\mathrm{ARIMA}(2,0,0)(0,1,1)_{168}$}
		\label{fig:mems:arima:200011}
	\end{subfigure}
	\begin{center}
		\caption{ARIMA forecasts}
		\label{fig:mems:arima}
	\end{center}
\end{figure}

>>>>

\begin{figure}[h]
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=\linewidth]{project.uccs_files/figure-latex/arima-35}
		\caption{ACF and PACF plots}
		\label{fig:arima-26}
	\end{subfigure}
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=\linewidth]{project.uccs_files/figure-latex/arima-32}
		\caption{Q-Q plot}
		\label{fig:arima-24}
	\end{subfigure}
	\begin{center}
		\caption{Plots for $\mathrm{ARIMA}(2,0,0)(0,1,1)_{168}$}
		\label{fig:arima}
	\end{center}
\end{figure}

@@

\begin{figure}[h]
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=1\linewidth]{project.uccs_files/figure-latex/arima-37}
		\caption{$\mathrm{ARIMA}(2,0,0)(0,1,1)_{168}$}
		\label{fig:arima-forecast:200011}
	\end{subfigure}
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=1\linewidth]{project.uccs_files/figure-latex/arima-69}
		\caption{$\mathrm{ARIMA}(3,1,1)(0,1,1)_{168}$}
		\label{fig:arima-forecast:412011}
	\end{subfigure}
	\begin{center}
		\caption{ARIMA forecasts}{\footnotesize$\mathrm{ARIMA}(4,1,2)(0,1,1)_{168}$ behaves like $\mathrm{ARIMA}(3,1,1)(0,1,1)_{168}$ with faster increasing variablity}
		\label{fig:arima-forecast}
	\end{center}
\end{figure}

@@

\begin{figure}[h]
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=1\linewidth]{"project.mems_files/figure-latex/arima-21"}
		\caption{$\mathrm{ARIMA}(0,1,1)(0,1,1)_{168}$}
		\label{fig:mems:arima:011011}
	\end{subfigure}
	\begin{subfigure}{.5\linewidth}
		\includegraphics[width=1\linewidth]{"project.mems_files/figure-latex/arima-13"}
		\caption{$\mathrm{ARIMA}(2,0,0)(0,1,1)_{168}$}
		\label{fig:mems:arima:200011}
	\end{subfigure}
	\begin{center}
		\caption{ARIMA forecasts}
		\label{fig:mems:arima}
	\end{center}
\end{figure}
